Resource-use and the Value-Productivity Tradeoff in Australian Winegrowing Regions

### 2023-07-07 article.tex
Up to general linear model in result section.

Linear relationships between variables were explored using Pearson Correlation Coefficients. Values for these coefficients are a measure of the linear relation between two variables; this measure is scale between -1 and 1, indicating the strength of the relationship. Transforming the data prior to calculating these values changes several things: The logarithmic transform of the data changes the interpretation of the coefficients to percentage changes, such that a coefficient will be indicative of the ratio a variable will change in percentage compared to a one percent increase in the other; being scaled by standard deviation this increase will be relative to the standard deviation, making it a percent of that variables standard deviation. Scaling by standard deviation also makes the Pearson Correlation Coefficient equal to the covariance of the two variables. 
%
This was undertaken for data on the original scale (see Table 2) and for data as a logarithmic transform (see Table 3). Strong relationships were found to be present, as all P-values were considered significant (< 2.200E-16, see Tables 2 and 3), except for the non-transformed values for water used (see Table 4). The logarithmic transforms showed the strongest correlations, this was likely due to a skew caused by a greater number of smaller vineyards within the dataset (see Table 5).

@@

\subsection{General Linear Models}
Models 1 and 2 showed significant relationships between each of the predictors and their response variables (see Tables 6 and 7). Variables in models 3 and 4 reported similar significance; except for scope 1 emissions (see Tables 8 and 9). Scope one emissions was included in all models to directly compare the response variables as ratios of vineyard size to raw values. Even though not significant within models 3 and 4, when using the Pearson Correlation Coefficients, scope one emissions was strongly correlated to every Model's response variable; this was especially so for Model 1 and 4 (Yeild and average price per tonne as a ratio to area harvested, respectively).

>>>>

Linear relationships between variables were explored using Pearson Correlation Coefficients. Values for these coefficients reflect the linear relation between two variables, on a scale between -1 and 1; the magnitude and sign of a coefficient indicates the strength of the relation, and whether the relation is positive or negative respectively. This was undertaken for data on the original scale (see Table 2) and for data as a logarithmic transform (see Table 3). The logarithmic transforms showed the strongest correlations, this was likely due to a skew caused by a greater number of smaller vineyards within the dataset (see Table 5). Transforming data prior to calculating the coefficients changes several things: The logarithmic transform of the data alters the interpretation of the coefficients to percentage change \- a coefficient will be indicative of the change in percentage of one variable compared to the other; scaling by standard deviation also changes this interpretation to be a percentage of that variables standard deviation. Scaling by standard deviation also makes the Pearson Correlation Coefficient equal to the covariance of the two variables. A correlation of 1 would indicate that given the change of one variable by one percentage of its standard deviation, the other variable would change by one percent of its standard deviation; the importance of this is the unitless nature of these relationships and that it can be translated directly to any case that has a well known distribution.
To determine if a coefficient was indicative of a strong relationship, P-values were used. P-values reflect the significance of a given correlation coefficient when considering its relation to sample size via its incorporation as an element of standard error. Strong relationships were found to be present, as all P-values were considered significant (< 2.200E-16, see Tables 2 and 3), except for the non-transformed values for water used (see Table 4).

@@

\subsection{General Linear Models}
% What are these tables?
% what are these models?
% What are F values?
% Why are some significant?
% What are degrees of freedom
% what are mean sq values?
% What are sum sq values?
% What are the ramifications of any of this???
% Break this down into each model separately!! DO NOT GENERALISE
Models 1 and 2 showed significant relationships between each of the predictors and their response variables (see Tables 6 and 7).
% Why are they significant?
Variables in models 3 and 4 reported similar significance; except for scope 1 emissions (see Tables 8 and 9). Scope one emissions was included in all models to directly compare the response variables as ratios of vineyard size to raw values. Even though not significant within models 3 and 4, when using the Pearson Correlation Coefficients, scope one emissions was strongly correlated to every Model's response variable; this was especially so for Model 1 and 4 (Yeild and average price per tonne as a ratio to area harvested, respectively).
